\textsc{Ferret Miner}: A Process Mining Case Study

### 2022-12-12 paper/paper.tex
Minor change.

\begin{abstract}
The objective of this project is to analyze event data logs from
the travel reimbursement process at Eindhoven University of Technology
(ETU/c), identify bottlenecks in the process, and
seek improvement to its efficiency.
We process and filter the event data, and then generate simplified and
representative process models to help locate where
the most time-consuming and impactful critical tasks are.
Our analysis suggests that
improvement in the supervisor appproval and payment handling activities 
could significantly
reduce the time processing the travel reimbursement.
\end{abstract}

@@

This project is a process mining case study designed to
identify patterns,
delays and bottlenecks that obstruct the efficient flow of the process
activities. Specifically, we studied a dataset with
real-life event log data from the travel reimbursement process at
Eindhoven University of Technology (ETU/e).
The event logs provide a detailed record of the travel reimbursement process,
including important attributes such as identification, resource,
timestamp, permits, payment and budgetting information, and event labels.
Students or staff would submit their reimbursement application,
provide suppport documentation (if traveling internationally), wait for
reimbursement decision and subsequent payment, and possibly deal with
rejection and resubmission. All of these information is captured in the
event log.
Collectively, these information provided a substantial amount of detail
into the process. 
The data was obtained from 
the annual Business Process Intelligence Challenge (BPI Challenge)
as part of
the 2020 International Conference on Process Mining held in Padova, Italy
\cite{BPI2020}, and has been
pre-processed and anonymized for research purpose.

@@

Furthermore, we are very interested in the evaluation and application
of a relatively new process mining technique based on
the Python-based process mining library called \textsc{pm4py}
developed by Berti, van Zelst, and van der Aalst \cite{BeZe2019}.
According to the authors,
\textsc{pm4py} is a modern, open-source, and emerging platform developed
specifically for the data science community. Prior to the turn of the
millenium,
there were hardly any tooling for process mining, but
since then a slew of software tools, both open-source
(ProM and Apromore) and commercial (Disco, Celonis, and ProcessGold),
have been developed. Yet, many were proprietary, hard to extend,
hiding behind graphical user interfaces, or (worst yet) all of the above.
The mindset of process mining
tooling contrasted greatly with the modern philosophy of data science R\&D,
which put significant emphasis on openness and extensibility.
\textsc{pm4py} was developed to bridge the gap
between old-style process mining and modern data science
capabilities including
\texttt{Pandas}, \texttt{NumPy}, \texttt{scikit-learn}.

@@

Most process mining publications are dedicated mainly to the enhancement
of novel methodologies and algorithms with significant emphasis on the
control-flow discovery area \cite{van2004}. However, the public services area
has been fruitful ground
for process mining development research. For instance, a
Genetic Miner approach was tested by Alves de Madeiros et al. \cite{deMe2007}
in Dutch municipalities. Additionally, van del Aalst et al. \cite{RoDJ2009}
applied an analysis of organizations in another municipality process.
Rozinat et al. \cite{RoMa2009} evaluated process models in two different case
studies on the public sector.

Nonetheless, all these research
applications are focused to validate and assess rather than enhance the
process. Implementation of process mining approaches have been also
developed in the private domain. Distinct discovery approaches were
deployed by Goedertier et al. \cite{GoDW2011} in the telecom field. Also, Mans
et al. \cite{MaSc2008} and Rebuge and Ferreira \cite{ReBu2012} created a convoluted
process mining method to resolve the tracking of patients within the
healthcare industry.

The literature mentioned above provides the fundamentals of process mining from a general perspective. Each approach contributes significantly to the process mining study field, and in this paper, we focus on its application.

@@

We shall briefly describe our approach to answering the questions of
where the bottlenecks are. We would first properly clean the event logs,
and then build a model that best captures the behavior of the
process (in other words, to mine the process), making the proper tradeoff
between robustness, accuracy, and coverage.  Then, we will use the
chosen model to answer the questions we have in mind.

We shall note that process mining is a relatively new techniques, and
as such we spent a disproportional amount of time ramping up the project.
While \textsc{pm4py}, in essence an academic software,
was a great choice compared to other proprietary enterprise software
due to its focus on discovery algorithms and availability on Python,
it was nonetheless relatively immature and early in its development, and
hence suffered from instability. The visualization capability was clearly
inadequate, and it offered very little flexibility as far as exploration
is concerned.

@@

In this section we will discuss about data, how we preprocessed the data, which model we used, how we reach the result and disscuss about the result.

@@

After clear understanding of the question we got to know that we had to
 find bottleneck in travel declaration.
After reviewing the data provided to us we  decided to go with the domestic
and internation declaration.
Both the dataset are in XES format,
an XML-based standard for event logs \cite{XES2021}.
It contains the information regarding the process that is
they contains event log. The events are organized in a two-level hierarchy --
the log is made of a collection of cases (also known as traces in technical
term), and each case is made of a collection of events. Both cases and
events are extensible constructs to allow for maximum flexibility in
modeling events for different needs.

As we imported the logs into Python via \textsc{pm4py}, in their simplest form the
log is organized into a Python dataframe, a key construct of
\texttt{Pandas}, the popular Python Data Analysis Library. However, as
dataframes are not hierarchical, \textsc{pm4py} flattene the log such that the
cases, and case attributes, become attributes of events. Therefore, if
there are $A_c$ case attributes in the case, and $A_e$ event attributes in the
XML specification, after \textsc{pm4py} import, we obtain a dataframe 
with $N$ observations, a total of $A_c + A_e$ attributes.

@@

While we did not find any missing value per se (as far
as what \texttt{Pandas} is concerned), we did find columns with values of
the form ``\texttt{UNKNOWN}'' or ``\texttt{MISSING}'' as string. We
carefully evaluated what to do with these attributes on a case-by-case
basis. For example, we could drop the column (attribute), drop the row
(event), fill the missing values, or simply ignore the column.

@@

\begin{figure*}[htbp]
\centerline{\includegraphics[width=0.90\textwidth]{images/domestic.png}}
\caption{DFG Model for Domestic Reimbursement.}
\label{fig-domestic}
\end{figure*}

\begin{figure*}[htbp]
\centerline{\includegraphics[width=0.90\textwidth]{images/international.png}}
\caption{DFG Model for International Reimbursement.}
\label{fig-international}
\end{figure*}

>>>>

\begin{abstract}
This project is a process mining case study designed to
identify patterns,
delays and bottlenecks that obstruct the efficient flow of the process
activities. Specifically, our
objective is to analyze event data logs from
the travel reimbursement process at Eindhoven University of Technology
(ETU/c), identify bottlenecks in the process, and
seek improvement to its efficiency.
We process and filter the event data, and then generate simplified and
representative process models to help locate where
the most time-consuming and impactful critical tasks are.
Our analysis suggests that
improvement in the supervisor appproval and payment handling activities 
could significantly
reduce the time processing the travel reimbursement.
\end{abstract}

@@

In this process mining case study, we are tasked with
studying a dataset with
real-life event log data from the travel reimbursement process at
Eindhoven University of Technology (ETU/e). Through analyzing the event
logs and mining the business process beneath the events, we seek to
identify and suggest remedy to address deficiencies in the reimbursement
process.
The event logs provide a detailed record of the travel reimbursement process,
including important attributes such as identification, resource,
timestamp, permits, payment and budgetting information, and event labels.
Students or staff would submit their reimbursement application,
provide suppport documentation (if traveling internationally), wait for
reimbursement decision and subsequent payment, and possibly deal with
rejection and resubmission. All of these information is captured in the
event log.
Collectively, these information provided a substantial amount of detail
into the process. 
The data was obtained from 
the annual Business Process Intelligence Challenge (BPI Challenge)
as part of
the 2020 International Conference on Process Mining held in Padova, Italy
\cite{BPI2020}, and has been
pre-processed and anonymized for research purpose.

@@

Furthermore, we are very interested in the evaluation and application
of a relatively new process mining technique based on
the Python-based process mining library called \textsc{pm4py}
developed by Berti, van Zelst, and van der Aalst \cite{BeZe2019}.
According to the authors,
\textsc{pm4py} is a modern, open-source, and emerging platform developed
specifically for the data science community. Prior to the turn of the
millenium,
there were hardly any tooling for process mining, but
since then a slew of software tools, both open-source
(\textsc{prom} and \textsc{apromore}) and commercial
(\textsc{disco}, \textsc{celonis}, and \textsc{processgold}),
have been developed. Yet, many were proprietary, hard to extend,
hiding behind graphical user interfaces, or (worst yet) all of the above.
The mindset of process mining
tooling contrasted greatly with the modern philosophy of data science R\&D,
which put significant emphasis on openness and extensibility.
\textsc{pm4py} was developed to bridge the gap
between old-style process mining and modern data science
capabilities including
\textsc{pandas}, \textsc{numpy}, \textsc{scikit-learn}.

@@

Most process mining publications are dedicated mainly to the enhancement
of novel methodologies and algorithms with significant emphasis on the
control-flow discovery area \cite{van2004}. However, the public services area
has been fruitful ground
for process mining development research. For instance, a
Genetic Miner approach was tested by Alves de Madeiros et al. \cite{deMe2007}
in Dutch municipalities. Additionally, van del Aalst et al. \cite{RoDJ2009}
applied an analysis of organizations in another municipality process.
Rozinat et al. \cite{RoMa2009} evaluated process models in two different case
studies on the public sector.
Nonetheless, all these research
applications are focused to validate and assess rather than enhance the
process.

Implementation of process mining approaches have also been deployed in
the private domain. Distinct discovery approaches were
deployed by Goedertier et al.~\cite{GoDW2011} in the field of
telecommunication. Mans
et al.~\cite{MaSc2008} and Rebuge et al.~\cite{ReBu2012} both
evaluated process mining methods
to resolve the tracking of patients within the healthcare industry.

@@

We shall briefly describe our approach to answering the questions of
where the bottlenecks are. We would start with a thorough analysis and
cleaning of the event logs, and then
build a model that best captures the behavior of the
process, making the proper tradeoff
between robustness (does the model capture the intent of the process),
and coverage (what fraction of the use cases are captured).
 Then, we will use the
chosen model to answer the questions we have in mind.

We shall note that process mining is a relatively new techniques, and
as such we spent a disproportional amount of time ramping up the project.
While we fully believe in the full potential of \textsc{pm4py} due to
its focus on algorithmic discovery and availability
on Python, it is
essentially still an academic software in its nascent stage, and 
hence suffers from instability. There is still plenty of room for
improvement in areas such as lack of control in visualization and
presentation, scanty documentation, and signs of immaturity in API design.

@@

In this section we will discuss about data,
how we preprocessed the data,
which model we used, and how
we reach the result and disscuss about the result.

@@

After a thorough review of what our tasks entail, we decided to focus
exclusively on the domestic and international travel event logs in order
to identify the process bottleneck.  Both event logs
were provided to us in XES format,
an XML-based standard for event logs \cite{XES2021}, which can
be easily parsed using \textsc{pm4py}.
The events are organized as a two-level hierarchy as follows:
An event log is made of a collection of cases
(also known as traces in technical
term), and each case is made of a collection of events. Both cases and
events are extensible constructs to allow for maximum flexibility in
modeling events for different needs.

The event logs provide a detailed record of the travel reimbursement process,
including important attributes such as identification, resource,
timestamp, permits, payment and budgetting information, and event labels.
Students or staff would submit their reimbursement application,
provide suppport documentation (if traveling internationally), wait for

As we imported the logs into Python via \textsc{pm4py}, in their simplest form the
log is organized into a Python dataframe, a key construct of
\textsc{pandas}, the popular Python Data Analysis Library. However, as
dataframes are not hierarchical, \textsc{pm4py} flattene the log such that the
cases, and case attributes, become attributes of events. Therefore, if
there are $A_c$ case attributes in the case, and $A_e$ event attributes in the
XML specification, after \textsc{pm4py} import, we obtain a dataframe 
with $N$ observations, a total of $A_c + A_e$ attributes.

@@

While we did not find any missing value per se (as far
as what \textsc{pandas} is concerned), we did find columns with values of
the form ``\texttt{UNKNOWN}'' or ``\texttt{MISSING}'' as string. We
carefully evaluated what to do with these attributes on a case-by-case
basis. For example, we could drop the column (attribute), drop the row
(event), fill the missing values, or simply ignore the column.

@@

\begin{figure*}[htbp]
\centerline{\includegraphics[width=0.70\textwidth]{images/domestic.png}}
\caption{DFG Model for Domestic Reimbursement.}
\label{fig-domestic}
\end{figure*}

\begin{figure*}[htbp]
\centerline{\includegraphics[width=0.70\textwidth]{images/international.png}}
\caption{DFG Model for International Reimbursement.}
\label{fig-international}
\end{figure*}
